\emph{MixFishSim}: highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2019-06-27 write_up/mixfishsim_ecolmod.tex
Text update

\deleted[id=PD]{the habitat}We first define\added[id=PD]{d} a Gaussian random
field process\todo{\added[id=JJ]{Not clear how habitat/GRF affect local
		abundances, only have $B_{y,d}$}\added[id=PD]{Have included
		cell reference, $c$ to make spatial link explicit}}, $\{S(c) :
c \in \mathbb{R}^2\}$, \deleted[id=PD]{that is a stochastic process} where
\added[id=PD]{for} any set of cells $c_{1}, \dots, c_{n}$ \deleted[id=PD]{where
	for each $c_{i} \in \mathbb{R}^2$}, the joint distribution of $S =
\{S(c1),\dots S(c_{n})\}$ is multivariate Gaussian. The distribution is
specified by its \textit{mean function}, $\mu(c) = E[S(c)]$ and its
\textit{covariance function}\todo{\added[id=JM]{Introduce the gamma function,
		and why this covariance structure? Why correlate values in the
		random field?}\added[id=PD]{to allow populations to have
		different aggregation densities: have tried to clarify}},
$\gamma(c,c') = Cov\{S(c),S(c')\}$ \citep{Diggle2007}.\\

The covariance structure affects the smoothness of the surfaces which the
process generates\replaced[id=PD]{;}{, and} we used the \textit{Matérn}
\deleted[id=PD]{family of}covariance structure\deleted[id=PD]{s},
\replaced[id=PD]{where}{one where} the correlation strength weakens with
distance\deleted[id=PD]{(i.e. the correlation between $S(x)$ and $S(x')$
	decreases as the distance $u = ||x - x'||$ increases)}.
\added[id=PD]{This enables us to model the spatial autocorrelation observed in
	animal populations where density is more similar in nearby locations
	\citep{Tobler1970, F.Dormann2007}} and we change the parameters to
implement different spatial structures for the populations. The \textit{Matérn}
correlation is a two-parameter family where: 
	\begin{center}
		$\rho(u) = \{2^{\kappa -
			1}\Gamma{\kappa}\}^{-1}(u/\phi)^{\kappa}K_{\kappa}(u/\phi)$
	\end{center}
$K_{\kappa}(.)$ is a modified Bessel function of order $\kappa$, $\phi >
0$ is a scale parameter with the dimensions of distance, and $\kappa > 0$,
called the order, is a shape parameter which determines the smoothness of the
underlying process (Figure \ref{S-fig:16}). \\

@@

Several studies \citep[e.g.][]{Hutton2004, Tidd2012, Girardin2015} have
confirmed past activity and past catch rates are strong predictors of fishing
location choice. For this reason, the fleet dynamics sub-model
include\replaced[id=PD]{d}{s} a learning component, where a vessel's initial
fishing location in a trip \replaced[id=PD]{wa}{i}s based on selecting from
previously successful fishing locations. This \replaced[id=PD]{wa}{i}s achieved
by \added[id=PD]{calculating an expected revenue based on the catches from
	locations fished} in the preceding trip as well as the same month
periods in previous years and the travel costs from the port to the fishing
grounds, and choosing randomly from the top 75 \% of fishing events
\replaced[id=PD]{as defined by the expected profit}{in value}. Simulation
testing indicated that this learning increased the mean value of catches for
the vessels, over just relying on the correlated random walk
\todo{\added[id=JJ]{Correlated random walk of what}} function \added[id=PD]{as
	described for the 'within trip' decisions below} (MIGHT NEED TO INCLUDE
IN SUPPLEMENTARY).

@@

\section{Calculation - used by journal / Parameterisation}

\subsection{Population parametrisation}

We parametrised the simulation model for four populations with different
population demographics; growth rates, natural mortality and recruitment
functions (Table \ref{tab:1}). Habitat preference (Figure \ref{S-fig:1}) and
temperature tolerances (Figures \ref{S-fig:3}, \ref{S-fig:4}) were unique to
each population resulting in differently weekly distribution patterns (Figures
\ref{S-fig:5}-\ref{S-fig:7}). In addition, each of the populations has two
defined spawning areas which result in the populations moving towards these
areas in pre-defined weeks (Figure \ref{S-fig:2}) with population-specific
movement rates (Table \ref{tab:1}). The realised movement of the populations
for a number of weeks is shown in Figure \ref{S-fig:9} while the realised daily
fishing mortality are shown in Figure \ref{S-fig:10}.

@@

An example of the realised fleet movements for a single vessel during a single
trip are given in Figure \ref{S-fig:11}, while Figure \ref{S-fig:12} shows
multiple trips for a single vessel, \added[id=PD]{Figure} \ref{S-fig:13} the
vessel movements for several trips overlaid on the value field (sum of the
population densities $\times$ price), \added[id=PD]{Figure} \ref{S-fig:14} shows
fishing locations for an entire fleet of 20 vessels for a single trip,
\replaced[id=PD]{and Figure}{while} \ref{S-fig:15} shows an example of the step
function realisation and turning angles from the correlated random
walk.\todo{\added[id=JJ]{Move some of the supplementary figures to the
		manuscript}}

>>>>

\deleted[id=PD]{the habitat}We first define\added[id=PD]{d} a Gaussian random
field process\todo{\added[id=JJ]{Not clear how habitat/GRF affect local
		abundances, only have $B_{y,d}$}\added[id=PD]{Have included
		cell reference, $c$ to make spatial link explicit}}, $\{S(c) :
c \in \mathbb{R}^2\}$, \deleted[id=PD]{that is a stochastic process} where
\added[id=PD]{for} any set of cells $c_{1}, \dots, c_{n}$ \deleted[id=PD]{where
	for each $c_{i} \in \mathbb{R}^2$}, the joint distribution of $S =
\{S(c1),\dots S(c_{n})\}$ is multivariate Gaussian with a \textit{Matérn}
\deleted[id=PD]{family of}covariance structure\deleted[id=PD]{s},
\replaced[id=PD]{where}{one where} the correlation strength weakens with
distance\deleted[id=PD]{(i.e. the correlation between $S(x)$ and $S(x')$
	decreases as the distance $u = ||x - x'||$ increases)}.
\added[id=PD]{This enables us to model the spatial autocorrelation observed in
	animal populations where density is more similar in nearby locations
	\citep{Tobler1970, F.Dormann2007}} and we change the parameters to
implement different spatial structures for the populations. \\

@@

Several studies \citep[e.g.][]{Hutton2004, Tidd2012, Girardin2015} have
confirmed past activity and past catch rates are strong predictors of fishing
location choice. For this reason, the fleet dynamics sub-model
include\replaced[id=PD]{d}{s} a learning component, where a vessel's initial
fishing location in a trip \replaced[id=PD]{wa}{i}s based on selecting from
previously successful fishing locations. This \replaced[id=PD]{wa}{i}s achieved
by \added[id=PD]{calculating an expected revenue based on the catches from
	locations fished} in the preceding trip as well as the same month
periods in previous years and the travel costs from the port to the fishing
grounds, and choosing randomly from the top 75 \% of fishing events
\replaced[id=PD]{as defined by the expected profit}{in value}.

@@

\section{Parameterisation}

\subsection{Population models}

We parametrised the simulation model for four populations with different
demographics; growth rates, natural mortality and recruitment functions (Table
\ref{tab:1}). Habitat preference (Figure \ref{S-fig:1}) and temperature
tolerances (Figures \ref{S-fig:3}, \ref{S-fig:4}) were unique to each
population resulting in differently weekly distribution patterns (Figures
\ref{S-fig:5}-\ref{S-fig:7}). In addition, each of the populations has two
defined spawning areas which result in the populations moving towards these
areas in pre-defined weeks (Figure \ref{S-fig:2}) with population-specific
movement rates (Table \ref{tab:1}). The individual habitat preferences and
thermal tolerances results different spatial habitat use for each population
(Figure \ref{S-fig:9}) and consequently different seasonal exploitation
patterns (Fishing mortality in Figure \ref{S-fig:10}).

@@

It can be seen from a single vessels movements during a trip that the vessel
exploits four different fishing grounds, three of them multiple time (Figure
\ref{S-fig:11}), while across multiple trips fishing grounds that are further
apart are fished (Figure \ref{S-fig:12}). These different locations relate to
areas where the highest revenue were experienced, as shown by
\added[id=PD]{Figure} \ref{S-fig:13}, which shows several trips for the vessel
overlaid on the value field (sum of the population densities $\times$ price).
Vessels from the same fleet (and therefore targeting preference) exploit
similar but slightly different fishing grounds depending on their own personal
experience during the explore phase of the fishery (\added[id=PD]{Figure}
\ref{S-fig:14}), which is the result of the correlated random walk step
function, with distance moved during the exploitation phase related to the
revenue experienced on the fishing ground (\replaced[id=PD]{Figure}{while}
\ref{S-fig:15}).\todo{\added[id=JJ]{Move some of the
		supplementary figures to the manuscript}}
